\documentclass[a4paper,10pt]{article}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  STARTING HERE, DO NOT TOUCH ANYTHING 
%%%%%%% --------------------------------------------------------------------------------------

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{csquotes}
\usepackage{tabularx}
\hypersetup{colorlinks=true,urlcolor=black}
\usepackage[12pt]{moresize}
\usepackage{setspace}
\usepackage{fontspec}
\usepackage[inline]{enumitem}
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\usepackage{anyfontsize}

%%%% Set Margins
\usepackage[margin=1cm, top=1cm]{geometry}

%%%% Set Fonts
\setmainfont[
BoldFont=SourceSansPro-Semibold.otf,
ItalicFont=SourceSansPro-RegularIt.otf
]{SourceSansPro-Regular.otf}
\setsansfont{SourceSansPro-Semibold.otf}

%%%% Set Page
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%%%% Set URL Style
\urlstyle{same}

%%%% Set Indentation
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%%%% Set Secondary Color
\definecolor{UI_blue}{RGB}{32, 64, 151}

%%%% Define New Commands
\usepackage[style=nature, maxbibnames=3]{biblatex}
\addbibresource{Publications.bib}

%%%% Bold Name in Publications
\renewcommand*{\mkbibnamegiven}[1]{%
\ifitemannotation{highlight}
{\textbf{#1}}
{#1}}

\renewcommand*{\mkbibnamefamily}[1]{%
\ifitemannotation{highlight}
{\textbf{#1}}
{#1}}

%%%% Set Sections formatting
\titleformat{\section}{
\color{UI_blue} \scshape \raggedright \large 
}{}{0em}{}[\vspace{-10pt} \hrulefill \vspace{-6pt}]

%%%% Set Subtext Formatting
\newcommand{\subtext}[1]{
#1\par\vspace{-0.2cm}}

%%%% Set Item Spacing
\setlist[itemize]{align=parleft,left=0pt..1em}

%%%% New Itemize "Zitemize" Formatting - tighter spacing than itemize
\newenvironment{zitemize}{
\begin{itemize}\itemsep0pt \parskip0pt \parsep1pt}
{\end{itemize}\vspace{-0.5cm}}

%%%% Define Skills Bold Formatting
\newcommand{\hskills}[1]{
\textbf{\bfseries #1} }

%%%% Set Subsection formatting
\titleformat{\subsection}{\vspace{-0.1cm} 
\bfseries \fontsize{11pt}{2cm}}{}{0em}{}[\vspace{-0.2cm}]

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  END OF "DO NOT TOUCH" REGION
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------

\begin{document}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  HEADER
%%%%%%% --------------------------------------------------------------------------------------
\begin{center}
    \begin{minipage}[b]{0.24\textwidth}
            Bengaluru, India \\
            (+91)9013799412 \\
            \href{mailto:mukundtiwari@outlook.com}{mukundtiwari@outlook.com} 
    \end{minipage}% 
    \begin{minipage}[b]{0.5\textwidth}
            \centering
            {\Huge Mukund Tiwari} \\ %
            \vspace{0.1cm}
    \end{minipage}% 
    \begin{minipage}[b]{0.24\textwidth}
            \flushright
            { \href{https://www.linkedin.com/in/mukund-tiwari-184203191/}{LinkedIn Profile} } \\
    \end{minipage}   
    
\vspace{-0.15cm} 

\end{center}

\section{Summary}
\subsection{}
    A DevOps Engineer with over five years of experience, specializing in high-scale AWS infrastructure, Kubernetes management, and automation. Successfully managed infrastructure scaling to handle millions of concurrent users, implemented robust CI/CD pipelines, and led critical cloud migrations. Expert in infrastructure as code, security best practices, and SRE principles.

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  WORK EXPERIENCE
%%%%%%% --------------------------------------------------------------------------------------
\section{Experience}        

%%%%%%% ----------------------------------- Role 5 ----------------------------------- %%%%%%%
\subsection*{Senior DevOps Engineer, Primetrace \hfill Dec 2024 --- Present} 
    \begin{zitemize}
        \item Led infrastructure scaling that handled 1.6M concurrent users and 6M DAU during peak events, supporting revenue of INR 4Cr in 36 hours, in a lean 2-person DevOps team.
        \item Conducted end-to-end load testing using Locust, achieving 3.6M TPM peak on backend APIs.
        \item Developed CI/CD automation using GitHub Actions and Slack integration, enabling Android team to trigger builds and Play Store deployments via slash commands.
        \item Enforced MFA for AWS Console access and implemented DB audit logging for non-app users via Pritunl VPN setup, strengthening security posture and compliance.
    \end{zitemize}

%%%%%%% ----------------------------------- Role 4 ----------------------------------- %%%%%%%
\subsection*{DevOps Engineer, Ollion \hfill Aug 2022 --- Nov 2024} 
    \begin{zitemize}
        \item Optimized infrastructure for Indonesian Digital Bank, saving \$230,000/year through EC2 rightsizing, VPC endpoint consolidation (90\% reduction), and Kubernetes cost optimization.
        \item Led migration of Indonesian OTT platform from GKE to AWS EKS, managing Terraform scripting, ingress controllers, and monitoring integration.
        \item Enhanced security across 80+ AWS accounts for UK-based media organization, creating automation scripts for issue identification.
        \item Executed cloud-to-cloud database migration from S3-Redshift to GCS-BigTable/BigQuery with secure VPN connectivity.
    \end{zitemize}

\subsection*{Senior Systems Engineer, Infosys \hfill Nov 2020 --- Aug 2022} 
    \begin{zitemize}
        \item Worked as Cloud Developer for the largest private bank in the world. Migrated on-prem Redis to Azure Cache for Redis and Go apps to AKS.
        \item Worked as Cloud Engineer for a Fortune 500, American MNC that provides financial technology services. Migrated on-prem apps to cloud (AKS) using Terraform.
        \item Received Certificate of Appreciation (INSTA AWARD) for cloud up-skilling efforts - 3 associate level certifications in 6 months, from Rajneesh Malviya, SVP-Service Offering Head-Financial Services.
        \item Ranked in the 98th percentile for Digital Quotient (DQ) points, a singular measure of digital proficiency, among employees at Infosys.
        %\item Trained as full stack developer. SQL Server - ASP.NET - Angular.
    \end{zitemize}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  CERTIFICATIONS
%%%%%%% --------------------------------------------------------------------------------------
\section{Certifications}
\begin{itemize}[leftmargin=*,itemsep=0pt,parsep=2pt]
    \item AWS Certified Solutions Architect - Associate (Nov 2024)
    \item Google Cloud Professional Cloud Security Engineer (Dec 2025)
    \item Google Cloud Professional Cloud Architect (Jan 2025)
    \item HashiCorp Certified: Terraform Associate (Nov 2024)
    \item Microsoft Certified: Azure Administrator Associate (Jun 2024)
\end{itemize}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  EDUCATION
%%%%%%% --------------------------------------------------------------------------------------
\section{Education}
\subsection*{Bachelor of Technology (B.Tech.), Electronics \& Communication Engineering (ECE), \hfill Oct 2020} 
{\normalsize \normalfont Maharaja Agrasen Institute of Technology, Delhi} \\
\subtext{CGPA: 7.33/10}
\vspace{0.1cm}
\subsection*{Class 12, CBSE, \hfill March 2016}
{\normalsize \normalfont Apeejay School, Pitampura, Delhi} \\
\subtext{Percentage: 94.6}
\vspace{0.2cm}

\end{document}
